%%%--------------------------------%%%
%%% Appendix
%%%--------------------------------%%%
\chapter{Appendix}
\label{ch:app-A}

\section{Survey Questionnaire}
\label{appquestionnaire}

Are you a project manager right now or have you been one over the course of the last year?
\begin{itemize}
	\item Yes
	\item No
\end{itemize}

Did you undertake any risk management measurements for projects within the last year?
\begin{itemize}
	\item Yes
	\item No
\end{itemize}

If not: Why not?
\begin{itemize}
	\item We usually don't do that.
	\item There wasn't enought time.
	\item The project was too small.
	\item Risk management is not useful.
	\item Other
\end{itemize}

Which of the following aspects did your risk management cover?
\begin{itemize}
	\item Risk identification
	\item Risk analysis
	\item Risk response planning
	\item Risk monitoring and controlling
\end{itemize}


Which kind of risk has caused you the most problems so far?
\begin{itemize}
	\item Lack of support
	\item Resources and personnel
	\item Scope and requirements
	\item Technology and design
	\item Communication and cooperation
	\item Discipline and motivation
	\item Other
\end{itemize}


How important do you think the following aspects of risk management are? (On a scale from 1 (Very important) to 5 (Not important at all) 
\begin{itemize}
	\item Risk identification
	\item Risk analysis
	\item Risk response planning
	\item Risk monitoring and controlling
\end{itemize}

Have you ever used any risk management software?
\begin{itemize}
	\item Yes
	\item No
\end{itemize}

If yes: Which tool did you use?

If not: Would you consider using risk management software in the future?
\begin{itemize}
	\item Yes
	\item No
\end{itemize}

How would you like to use risk managment software? (Multiple answers)
\begin{itemize}
	\item MacBook (Desktop)
	\item Windows-PC (Desktop)
	\item iPhone (Mobile)
	\item Android Phone (Mobile)
	\item Surface (Convertible)
	\item iPad (Mobile / Tablet)
\end{itemize}

Which aspect of risk management do you think a software would be most useful for?
\begin{itemize}
	\item Risk identification
	\item Risk analysis
	\item Risk response planning
	\item Risk monitoring and controlling
	\item Other
\end{itemize}


\section{Further Expansion Features}
\label{appfeatures}
The following features were suggested by project managers during the interview for prototype feedback:
\begin{itemize}
	\item Active Directory integration
	\item Microsoft Planner task export
	\item Altlassian Jira integration
	\item Risk export for operations team after the project is done
	\item Skill tags for team members
	\item Category tags for projects and risks
	\item Evaluation whether a project can be finished or risk cleanup should be done
\end{itemize}
